Learning can mediate the evolution of (cheap and costly) signals of quality

### 2022-07-25 Presentations/ISBE2022.Rmd
Conference presentation done ISBE2022

---
title: | 
    | Learning can mediate the evolution of 
    | (cheap and costly) signals of quality
author: "Andrés Quiñones"
bibliography: ../SocialMorphCue.bib
date: | 
    | 
    | 
    | ISBE - Stockholm 2022
    | August 2 - 2020
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
    \usepackage{xcolor}
---

@@

```{r,echo=FALSE,fig.align="center",out.width='40%'}

knitr::include_graphics("../Images/sexSelec.jpg")
knitr::include_graphics("../Images/dominance.jpg")
```

@@

```{r,echo=FALSE,fig.align='center',out.width='45%',fig.show='hold'}
knitr::include_graphics("../Images/HouseSparrow_strong.jpg")
knitr::include_graphics("../Images/HouseSparrow_weak.jpg")
```

@@

```
[@zahavi_Mate_1975;@grafen_Biological_1990]

@@

\vspace{-0.3cm}

### Conflict

\vspace{0.3cm}
\begin{columns}
\column{0.5\linewidth}
hawk-dove game
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.2cm} | >{\centering\arraybackslash}p{2.5cm} | >{\centering\arraybackslash}p{0.8cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

```{r,echo=FALSE,fig.align='center',out.width='60%'}
par(plt=posPlot(),las=1)
plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~
       seq(-1,1,length.out = 1000),type="l",xlab="",
     ylab = expression(p[w]),cex.lab=3,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
 mtext("Difference in quality",1,line = 4,cex = 3,las = 0)
lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~
       seq(-1,1,length.out = 1000),lwd=3,col="springgreen4")
legend("topleft",legend=c(2,10),col=c("red","springgreen4"),lwd=3,title = expression(beta),cex=2,bty="n")
```

@@

```{r, echo=FALSE,fig.align='center', out.width = '60%'}

@@

```{r, echo=FALSE,fig.align='center', out.width = '100%'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.height='90%'}
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn19_betCost5.png")
```

@@

```{r,out.width='45%',fig.show='hold'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png")
# knitr::include_graphics("../Images/cartoonRBF_InitAct.png")
nCenters<-6
interv<-1/(nCenters-1)
centers<-interv*seq(0,nCenters-1)
sigSq<-0.01
weights<-data.table(neutral=rep(0,nCenters),agressive=rep(-2,nCenters),
        peaceful=rep(2,nCenters),clever=rep(-0.69,nCenters))
rangx<-seq(0,1,length=1000)

@@

par(plt=posPlot()*0.95)
matplot(x=rangx,y=as.matrix(actor),type='l',col=c("black","red","blue","springgreen4"),lty=1,
     xlab="",ylab="",ylim=c(0,1.1),lwd=5,xaxt="s",cex.lab=1.5,cex.axis=2)
mtext(text = "p(dove)",2,line = 4,cex = 2.5,las=0)
mtext(text = "Badge size",1,line = 3.5,cex = 2.5)
points(y=logist(weights$neutral,alpha = 0,beta=1),x=centers,cex=3)
text(y = actor[1,]+0.1,x=rep(0.5,4),col=c("black","red","blue","springgreen4"),
     labels = names(weights),cex=2)
```

@@

```{r,echo=FALSE,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter_1.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter_.png")

@@

```{r, echo=FALSE,fig.align='center', out.height='80%',fig.show='hold'}
  knitr::include_graphics("../Images/BizarroParrot.jpg")
```

>>>>

---
title: | 
  | Learning can mediate the evolution of  (cheap and costly) signals of quality
author: |
  | Andrés Quiñones
institute: |
  | Universitè de Neuchâtel
bibliography: ../SocialMorphCue.bib
date: | 
  | 
  | 
  | ISBE - Stockholm 2022
output: 
  beamer_presentation: 
    fig_caption: yes
    keep_tex: yes
classoption: "aspectratio=169"
header-includes: 
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{amsmath} 
  \usepackage{graphicx}
  \usepackage{array}
  \usepackage{xcolor}
  \usepackage{makecell}
---

@@

```{r,echo=FALSE,fig.align="center",out.width='40%',fig.show='hold'}

knitr::include_graphics("../Images/sexSelec.jpg")
knitr::include_graphics("../Images/dominance2.jpg")
```

@@

```{r,echo=FALSE,fig.align='center',out.width='70%',fig.show='hold'}
knitr::include_graphics("../Images/houseSparrows.png")
# knitr::include_graphics("../Images/HouseSparrow_weak.jpg")
```

@@

```
\vspace{-0.3cm}
[@zahavi_Mate_1975;@grafen_Biological_1990]

@@

### Conflict: Hawk-Dove game

\begin{columns}
\column{0.5\linewidth}
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.6cm} | >{\centering\arraybackslash}p{1.5cm} | >{\centering\arraybackslash}p{1.5cm} }
& Hawk & Dove \\ \hline
Hawk & $ \makecell{p_w V\frac{-C}{2}  +  \\ (1-p_w) \frac{-C}{2}}$ & $V$ \\ \hline
Dove & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

```{r,echo=FALSE,fig.align='center',out.width='50%'}
par(plt=posPlot(),las=1)
plot(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 2)~
       seq(-1,1,length.out = 1000),type="l",xlab="",
     ylab = expression(p[w]),cex.lab=3,lwd=3,col="red",cex.axis=2,ylim=c(0,1))
 mtext("Difference in quality",1,line = 4,cex = 3,las = 0)
lines(logist(seq(-1,1,length.out = 1000),alpha = 0,beta = 10)~
       seq(-1,1,length.out = 1000),lwd=3,col="springgreen4")
legend("topleft",legend=c(2,10),col=c("red","springgreen4"),lwd=3,title = expression(beta),cex=2,bty="n")
```

@@

```{r, echo=FALSE,fig.align='center', out.width = '50%'}

@@

```{r, echo=FALSE,fig.align='center', out.width = '90%'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png")
```

@@

```{r, echo=FALSE,fig.align='center', out.width='90%'}
knitr::include_graphics("../Simulations/betCostEvol2_/evolDyn19_betCost5.png")
```

@@

```{r,out.width='45%',fig.show='hold'}
knitr::include_graphics("../Simulations/alphaAct_/alphaAct0.4learnDyn.png",)
# knitr::include_graphics("../Images/cartoonRBF_InitAct.png")
nCenters<-6
interv<-1/(nCenters-1)
centers<-interv*seq(0,nCenters-1)
sigSq<-0.01
weights<-data.table(neutral=rep(0,nCenters),agressive=rep(-2,nCenters),
        peaceful=rep(2,nCenters),clever=rep(-0.69,nCenters))
rangx<-seq(0,1,length=1000)

@@

par(plt=posPlot()*0.92)
matplot(x=rangx,y=as.matrix(actor),type='l',col=c("black","#E31A1C","dodgerblue2","green4"),lty=1,
     xlab="",ylab="",ylim=c(0,1.1),lwd=5,xaxt="s",cex.lab=1.5,cex.axis=2)
mtext(text = "p(dove)",2,line = 4,cex = 2.5,las=0)
mtext(text = "Badge size",1,line = 3.5,cex = 2.5)
points(y=logist(weights$neutral,alpha = 0,beta=1),x=centers,cex=3)
text(y = actor[1,]+0.1,x=rep(0.5,4),col=c("black","#E31A1C","dodgerblue2","green4"),
     labels = names(weights),cex=2)
```

@@

```{r,echo=FALSE,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter0_.png")

@@

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter1_.png")

```{r,out.width='90%',fig.show='hold'}
knitr::include_graphics("../Simulations/initAct_/indVarScatter2_.png")

@@

<!-- ```{r, echo=FALSE,fig.align='center', out.height='50%',fig.show='hold'} -->
<!--   knitr::include_graphics("../Images/BizarroParrot.jpg") -->
<!--   knitr::include_graphics("../Images/Socialnet1.png") -->
<!-- ``` -->

\begin{columns}[T]
 \column{0.7\linewidth}
  \includegraphics[height=0.8\textwidth]{../Images/BizarroParrot.jpg}
 \column{0.2\linewidth}
  \includegraphics[height=1.5\textheight]{../Images//Socialnet.png}
\end{columns}

### 2022-07-25 Presentations/ISBE2022.tex
Conference presentation done ISBE2022

]{beamer}

@@

  pdfauthor={Andrés Quiñones},

@@

\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}

@@

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones}
\date{\hfill\break
\hfill\break
ISBE - Stockholm 2022\\
August 2 - 2020}

@@

\begin{frame}{Social interactions}
\protect\hypertarget{social-interactions}{}
\begin{block}{The need to match partners with actions}
\protect\hypertarget{the-need-to-match-partners-with-actions}{}
\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \end{center}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}
\end{block}
\end{frame}

\begin{frame}{The effect of communication}
\protect\hypertarget{the-effect-of-communication}{}
\begin{block}{Badge of status}
\protect\hypertarget{badge-of-status}{}
\begin{center}\includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_strong} \includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_weak} \end{center}
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[height=0.35\textheight]{ISBE2022_files/figure-beamer/unnamed-chunk-4-1} \end{center}

@@

\begin{frame}{A model of communication in animal conflict}
\protect\hypertarget{a-model-of-communication-in-animal-conflict}{}
\vspace{-0.3cm}

\begin{block}{Conflict}
\protect\hypertarget{conflict}{}
\vspace{0.3cm}
\begin{columns}
\column{0.5\linewidth}
hawk-dove game
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.2cm} | >{\centering\arraybackslash}p{2.5cm} | >{\centering\arraybackslash}p{0.8cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-17-1} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-19-1} \end{center}

@@

\begin{frame}{Learning under honest signalling}
\protect\hypertarget{learning-under-honest-signalling}{}
\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn} \end{center}
\end{frame}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}
\end{frame}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status}{}
\begin{block}{Individual replicates: no badges}
\protect\hypertarget{individual-replicates-no-badges}{}
\begin{center}\includegraphics[width=19.44in,height=0.9\textheight]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}
\end{block}
\end{frame}

@@

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-1}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_1}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-2}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_}
\end{block}
\end{frame}

@@

\begin{frame}{Questions?}
\protect\hypertarget{questions}{}
\begin{center}\includegraphics[height=0.8\textheight]{../Images/BizarroParrot} \end{center}
\end{frame}

>>>>

  aspectratio=169]{beamer}

@@

@@

\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor} \usepackage{makecell}

@@

\title{Learning can mediate the evolution of (cheap and costly) signals
of quality}
\author{Andrés Quiñones}
\date{\hfill\break
\hfill\break
ISBE - Stockholm 2022}
\institute{Universitè de Neuchâtel}

@@

\begin{frame}{Social interactions}
\protect\hypertarget{social-interactions}{}
\begin{block}{The need to match partners with actions}
\protect\hypertarget{the-need-to-match-partners-with-actions}{}
\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \includegraphics[width=0.4\linewidth]{../Images/dominance2} \end{center}
\end{block}
\end{frame}

\begin{frame}{The effect of communication}
\protect\hypertarget{the-effect-of-communication}{}
\begin{block}{Badge of status}
\protect\hypertarget{badge-of-status}{}
\begin{center}\includegraphics[width=0.7\linewidth]{../Images/houseSparrows} \end{center}
\end{block}
\end{frame}

@@

\begin{center}\includegraphics[height=0.35\textheight]{ISBE2022_files/figure-beamer/unnamed-chunk-4-1} \end{center}
\vspace{-0.3cm}

@@

\begin{frame}{A model of communication in animal conflict}
\protect\hypertarget{a-model-of-communication-in-animal-conflict}{}
\begin{block}{Conflict: Hawk-Dove game}
\protect\hypertarget{conflict-hawk-dove-game}{}
\begin{columns}
\column{0.5\linewidth}
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.6cm} | >{\centering\arraybackslash}p{1.5cm} | >{\centering\arraybackslash}p{1.5cm} }
& Hawk & Dove \\ \hline
Hawk & $ \makecell{p_w V\frac{-C}{2}  +  \\ (1-p_w) \frac{-C}{2}}$ & $V$ \\ \hline
Dove & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-17-1} \end{center}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-19-1} \end{center}

@@

\begin{frame}{Learning under honest signalling}
\protect\hypertarget{learning-under-honest-signalling}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn} \end{center}
\end{frame}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol2_/evolDyn18_betCost5} \end{center}
\end{frame}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status}{}
\begin{block}{Individual replicates: no badges}
\protect\hypertarget{individual-replicates-no-badges}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol2_/evolDyn19_betCost5} \end{center}
\end{block}
\end{frame}

@@

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-1}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter0_}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-2}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter1_}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-3}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-3}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter2_}
\end{block}
\end{frame}

@@

\begin{frame}{Questions?}
\protect\hypertarget{questions}{}
\begin{columns}[T]
 \column{0.7\linewidth}
  \includegraphics[height=0.8\textwidth]{../Images/BizarroParrot.jpg}
 \column{0.2\linewidth}
  \includegraphics[height=1.5\textheight]{../Images//Socialnet.png}
\end{columns}
\end{frame}
